Type Error Telemetry at Scale

### 2023-09-28 programming23/paper.tex
count down/upgrades, fix bug, but need to double-check on server

  \begin{subfigure}[t]{\columnwidth}
    \begin{tabular}[t]{ll} \\
      \begin{tabular}[t]{r@{~~}r@{~}r}
        313,509 & \mnocheck{}   & [\pct{90.19}] \\
         32,902 & \mnonstrict{} & [\pct{ 9.47}] \\
            545 & \mstrict{}    & [\pct{ 0.16}] \\
            642 & mixed-mode    & [\pct{ 0.18}]
      \end{tabular}
      \begin{tabular}[t]{l@{~~}ll}
        \zerowidth{Among the mixed-mode sessions:} \\
        & 341 & contain a mode upgrade \\
        & 320 & contain a mode downgrade \\
        & 512 & contain modules with different modes
      \end{tabular}
    \end{tabular}
    \caption{Analysis mode(s) for the 347,598 sessions.}
    \label{f:total-sessions}
  \end{subfigure}

@@

\Cref{f:error-by-mode} shows how the type errors and forced strict errors
in the data are split across type analysis modes.
\FILL{} add averages.

@@

  \item[How often do creators turn analysis off?]
    Creators rarely disable type analysis after opting in.
    Only 320 of the \nK{340} sessions ($<\pct{1}$)
    switch to a weaker mode.
    \FILL{} are they downgrading from S or NS?
    %% FILL more insight if we match upgrades + downgrades in session?

>>>>

  \begin{subfigure}[t]{\columnwidth}
    \begin{tabular}[t]{ll} \\
      \begin{tabular}[t]{r@{~~}r@{~}r}
        313,509 & \mnocheck{}   & [\pct{90.19}] \\
         32,902 & \mnonstrict{} & [\pct{ 9.47}] \\
            545 & \mstrict{}    & [\pct{ 0.16}] \\
            642 & mixed-mode    & [\pct{ 0.18}]
      \end{tabular}
      \begin{tabular}[t]{l@{~~}ll}
        %% TODO numbers may be off by +- 100
        %%    & 341 & contain a mode upgrade \\
        %%    & 320 & contain a mode downgrade \\
        %%    & 512 & contain modules with different modes
        %%  they don't match out/error-density*hasdown.rkt
        %%  ??? counting downs instead of sessions with downs ???
        %% TODO fix throughout paper!
        \zerowidth{Among the mixed-mode sessions:} \\
        & 176 & contain a mode upgrade \\
        & 233 & contain a mode downgrade \\
        & 512 & contain modules with different modes
      \end{tabular}
    \end{tabular}
    \caption{Analysis mode(s) for the 347,598 sessions.}
    \label{f:total-sessions}
  \end{subfigure}

@@

\Cref{f:error-by-mode} shows how the type errors and forced strict errors
in the data are split across type analysis modes.

@@

  \item[How often do creators turn analysis off?]
    Creators rarely disable type analysis after opting in.
    Only 233 of the \nK{340} sessions ($<\pct{1}$)
    switch to a weaker mode.
    Most of these (\pct{75}) are downgrading from \mstrict{}
    rather than \mnonstrict{} mode.
    %% FILL more insight if we match upgrades + downgrades in session?

    %% upgrade
    %% 519 total sessions
    %% 176 with up
    %% #hash((nocheck . 0) (nonstrict . 44) (strict . 132))
    %%  nocheck : 0.00\%
    %%  strict : 75.00\%
    %%  nonstrict : 25.00\%
    %%
    %% downgrade
    %% 515 total sessions
    %% 233 with down
    %% #hash((nocheck . 0) (nonstrict . 64) (strict . 169))
    %%  nocheck : 0.00\%
    %%  strict : 72.53\%
    %%  nonstrict : 27.47\%
